---
title       : GDP per Capita by Countries
subtitle    : Course Project
author      : Thong B. Tran
job         : Developing Data Products
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Features 
Each year, the World Bank collects data from various sources and publish them on its website. This app
is an attempt to show the GDP per Capita of a few typical countries. In general, we have 

1. An interactive chart 
2. A summary of the GDP per Capita of the data
3. A data table to inspect each record.

---  

## Summary 
We can use `WDI`, an R package, in this project to get WDI data. Then we summarize it using the `summary` function in R 
 
```{r echo = TRUE}
library(WDI)
dat <- WDI(indicator='NY.GDP.PCAP.CD', 
           country=c('US','GB','JP','FR','DE','TH','VN','ID'), 
           start=1980, end=2014)
summary(dat)
```

---

## Chart
We can also visualize it by using `ggplot2` and `plotly`. The combination of these two library give you an interactive and beautiful chart.

```{r echo = TRUE, cache = FALSE, results = 'hide', warning = FALSE}
library(plotly)
library(ggplot2)
ggplot(data = dat, aes(year, NY.GDP.PCAP.CD, col = country)) + 
                                    geom_line() +     
                                    xlab('Year') + ylab('GDP per capita') + 
                                    labs(title = 'GDP Per Capita (current US$)')
ggplotly()
```

---

## Data table
We can easily make a beautiful data table with `DT` package.

```{r echo = TRUE, cache = FALSE, results = 'hide'}
library(DT)
datatable(data = dat)
```




